Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd

This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband]. The data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects. In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level [@kahan2020usbroadband]. After making such measurements, noise is added to data aggregations, preventing leakage about specific individuals in the dataset and ensuring differential privacy.

@@

What is more, Jack et al. [-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asians by district. It instead includes data of the corresponding shares of ELL and FRPL students by district, two demographic characteristics we did not consider in our analysis. This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and higher shares of Asian minorities, the former of which is known to face more days of school closed than the national average, were affected. We raise a question of whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status. Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023]. In fact, using multiple data sources external to the American school system, Fazlul et al. [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%. This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty in the Jack et al. [-@Jack_Oster_2] paper, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.

>>>>

This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband]. The data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects. According to Kahan [-@kahan2020usbroadband], in less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level. In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code. After making such measurements, noise is added to data aggregations using the SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.

@@

What is more, Jack et al. [-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asian students by district. It instead includes data of the corresponding shares of English Language Learners (ELL) and students eligible for Free and Reduced Price Lunch (FRPL) by district, two demographic characteristics we did not consider in our analysis. This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and higher shares of Asian minorities, the former of which is known to face more days of school closed than the national average, were affected. As an aside, we might also question whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status in Jack et al. [-@Jack_Oster_2]'s paper. Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023]. In fact, using multiple data sources external to the American school system, Fazlul et al. [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%. This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty in the Jack et al. [-@Jack_Oster_2] paper, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.
